Abstractions for Type-Level Programming

### 2022-05-14 symposium.tex
Minor

\noindent
The extractor pattern, |case date(y,m,d)|, replaces the need for manually indexing into the regular expression's capturing groups, and shields users from off-by-one error.

>>>>

\noindent
The extractor pattern, |case| |date(y,m,d)|, replaces the need for manually indexing into the regular expression's capturing groups, and shields users from off-by-one error.
